---
output: github_document
bibliography: references.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `polisciols`: Political Science OLS Replication Data

<!-- badges: start -->

<!-- badges: end -->

The goal of `polisciols` is to provide you with programmatic access to data that address political science questions.

## Installation

You can install the development version of polisciols from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hgoers/polisciols")
```

## Using `polisciols`

To use the data and helpful documentation, you will need to load `polisciols` into your current R session. You can do this by running the following:

```{r}
library(polisciols)
```

## Introducing multiple linear regression

@appel2012 explore the relationship between post-conflict net FDI inflows and states' implementation of post-conflict justice (PCJ) institutions. They find that these institutions promote foreign investment in post-conflict states. Their empirical work can serve as a really clear introduction to multiple linear regression.

You can access their full data set by running the following:

```{r}
head(ebj)
```

You can replicate their full linear regression model by running the following:

```{r}

m <- lm(net_fdi_inflows ~ pcj + gdp_per_capita + gdp + gdp_per_capita_growth + cap_account_openness + ex_rate_fluc + labor + f_life_exp + pol_constraints + polity2 + damage + conflict_duration + peace_agreement + victory + cold_war, 
        data = ebj)

summary(m)
```
